Performing graph-based clustering with rOpenScPCA

### 2024-12-13 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
speeling and less printing

Because clustering involves random sampling, it is important to set the random seed at the top of your analysis script or notebook to ensure reproducibilty.

@@

colData(sce)
```

@@

# Print the cell metadata
seurat_obj@meta.data
```

>>>>

Because clustering involves random sampling, it is important to set the random seed at the top of your analysis script or notebook to ensure reproducibility.

@@

head(colData(sce))
```

@@

# Print the cell metadata
head(seurat_obj@meta.data)
```
